Network Configuration Synthesis with Abstract Topologies

### 2016-11-06 paper/abstraction/paper.tex
add part of appendix

@@

@@

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     x       &::=& d.d.d.d/d & \textit{prefix} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

@@

>>>>

Foo

@@

\section{Start}

@@

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

@@

foo

  \end{minipage}
  \vspace{1em}
  \caption{Simplified BGP syntax.}
  \label{fig:abgp-syntax}
\end{figure}%

blah
